Collision rates of planetesimals near mean-motion resonances

### 2021-01-29 main.tex
Get rid of direct mention of St

%TRQ: do you need "St" here?  I don't think it's used elsewhere in the paper.St $\equiv t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions 
between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down. For 
the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr. There are a total of 15,000 planetesimals within this region, 
which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average. If the entire planetesimal population in this region were converted to 1 meter bodies 
with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$. The collision 
timescale would therefore decrease to $\sim$ 1 year, which is 2 orders of magnitude smaller than the drift timescale. As shown above, radial drift in the Stokes drag regime is maximized 
for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles. It is therefore not entirely clear if the Stokes drag law is appropriate here. 
Because of this, we also repeat the above calculation for bodies that experience Epstein drag. With this assumption, we find that radial drift is maximized for a cm-sized body and both the 
radial drift and collision timescale for bodies of that size decrease by a factor of 10 relative to the Stokes values. In both cases, collisions between maximally drifting bodies occur on a 
timescale two orders of magnitude shorter than the drift timescale. We therefore argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the 
physics before additional complexity is later added. We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.}

>>>>

\textbf{This occurs for bodies of the size at which $t_{s} \Omega$ = 1. In the Stokes drag regime at 3 au, this occurs for bodies of 1 meter in size. Following a similar 
calculation in \ref{sec:pl_drag} with a 1 m body, we find that an object of this size will drift across the 2:1 MMR on a timescale of $\sim$ 300 years. Although we do not model collisions 
between bodies of this size, a lower limit on the collision timescale for these objects can be obtained by extrapolating the planetesimal collision rate measured in our simulations down. For 
the e2m2 simulation, we find that 125 collisions occur within the libration width of the 2:1 MMR from T=2,000 yr to  T=5,000 yr. There are a total of 15,000 planetesimals within this region, 
which means that a single planetesimal undergoes a collision every $\sim$ 370,000 years on average. If the entire planetesimal population in this region were converted to 1 meter bodies 
with the same bulk density, the number density of bodies increases by a factor of $10^{15}$, while the geometric collision cross section decreases by a factor of $10^{10}$. The collision 
timescale would therefore decrease to $\sim$ 1 year, which is 2 orders of magnitude smaller than the drift timescale. As shown above, radial drift in the Stokes drag regime is maximized 
for bodies of 1 meter in size, which is only a factor of two larger than the mean free path of the gas particles. It is therefore not entirely clear if the Stokes drag law is appropriate here. 
Because of this, we also repeat the above calculation for bodies that experience Epstein drag. With this assumption, we find that radial drift is maximized for a cm-sized body and both the 
radial drift and collision timescale for bodies of that size decrease by a factor of 10 relative to the Stokes values. In both cases, collisions between maximally drifting bodies occur on a 
timescale two orders of magnitude shorter than the drift timescale. We therefore argue that it is reasonable and, indeed, best practice to start with such simple assumptions understand the 
physics before additional complexity is later added. We caution, however, that the collision timescale estimates provided here should be interpreted as lower limits.}
